Psyc 601 Multivariate Statistics Project

### 2013-08-15 writeups/proposal/proposal.tex
Thu commits
Former-commit-id: 1ce64a521fd9b977949af454a1f7e5f8d7d42be6 [formerly 3ea02c1fff9e15ea9e5c0dadbef51f0fb357c211]
Former-commit-id: 58456f74662c202a5ba643918aef26d7fe486927

\usepackage[american]{babel}
\usepackage[utf8]{inputenc}
%\usepackage[compact]{titlesec}

\usepackage{amssymb,amsmath}

@@

\usepackage{csquotes}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{bibliography.bib}

% If the toc is too detailed, try limiting the depth of printed sections in the TOC:
\setcounter{tocdepth}{2}

@@

TODO: Useful problem since real-time search on social media sites is growing \cite{Jansen2011}
TODO: Users want to be quickly connected to the content that they care about, with minimal amount of searching necessary, since the amount of generated content on these sites is so vast.

@@

TODO: Social media sites are composed almost entirely of human-generated content.
Users are searching through this content.

@@

\subsubsection{Modeling Hashtag Creation for a Single User}

@@

@@

@@

FIXME: Find cites for recommendation systems.

@@

\printbibliography

>>>>

\usepackage{textcomp}
\usepackage[american]{babel}
\usepackage[utf8]{inputenc}
%\usepackage[compact]{titlesec}

\usepackage{amssymb,amsmath}
\usepackage{setspace}

@@

\usepackage{csquotes}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber,doi=false,uniquename=false]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{bibliography.bib}

% If the toc is too detailed, try limiting the depth of printed sections in the TOC:
%\setcounter{tocdepth}{2}

@@

TODO: Useful problem since real-time search on social media sites is growing \cite{Jansen2011}
TODO: Social media sites are composed almost entirely of human-generated content.
Users are searching through this content.
TODO: Users want to be quickly connected to the content that they care about, with minimal amount of searching necessary, since the amount of generated content on these sites is so vast.

@@

@@

\subsubsection{Modeling Hashtag Use for a Single User}

@@

Grown in need with the growth of the web.
Users on a site need access to specific pieces of information, and the site contains much more information than they can process / care about.
Recommendation systems are used to tailor the presented information to what is relevant to the user.
\cite{Pazzani2007}

\subsubsection{Hashtags for Recommendation Systems}

@@

Previous research focused on StackOverflow, Google+, and Twitter.
Google+ has deployed automatic tagging of posts.

@@

TODO: None that we are aware of.

@@

\begingroup
\setstretch{1}
\setlength\bibitemsep{12pt}
\printbibliography
\endgroup
